Fluid-mechanical erosion creates anisotropic porous media

### 2022-06-02 docs/PhysicsPaper/StokesErosion.tex
NM

Integrating \eqref{q1} over the porous-medium domain $[-1, 1] \times [-1,1]$, applying the fundamental theorem of calculus, and rearranging gives
\begin{equation}
k_{11} = \frac{2U}{\pup - \pdn}
\end{equation}
This exact formula gives the permeability in terms of the total flux $U$ and measurements of the upstream/downstream pressure.

@@

The hydrodynamic drag on the collection of bodies is obtained by integrating the surface traction over the boundary $\gamma$. The surface traction is given by 
\begin{equation}
- \stress \, \nn = p \nn + \tau \ss
\end{equation}
where the negative sign is a consequence of choosing the normal vector $\nn$ pointing {\em into} the bodies. The total drag on the collection of bodies is thus
\begin{equation}
\FD =  - \int_{\gamma} \stress \, \nn \, ds =  \int_{\gamma} p \nn + \tau \ss \, ds
\end{equation}

@@

@@

The boundary integral on the right-hand-side of \eqref{divthm} has contributions from the boundaries of the erodable bodies $\gamma$ and from the outer boundary $\Gamma$, since $\partial \Omega = \gamma \cup \Gamma$. In particular, the total drag exerted by the erodable bodies is given by
\begin{equation}
\FD = -\int_{\gamma} \stress \cdot \nn \, ds
\end{equation}
We will mostly be interested in the horizontal drag $\FD \cdot \ex$. \\

Consider now the contribution to \eqref{divthm} from the outer boundary $\Gamma$. The horizontal component of this term is
\begin{align}
\ex \cdot \int_{\Gamma} \stress \cdot \nn \, ds = 
& \int_{-1}^{1} p(-x_0, y) - p(x_0, y) - 2\mu (u_x(-x_0,y) - u_x(x_0,y)) \, dy \, + \\
& \int_{-x_0}^{x_0} \mu (u_y(x,1) - u_y(x,-1)) dx
\end{align}
If we take $x_0$ sufficiently far away, then the viscous terms involving $u_x$ will become small as the velocity field tends to a uniform flow. Meanwhile, the contribution from the pressure is well approximated by the upstream and downstream average pressures $\pup$ and $\pdn$ as introduced in the previous section. This gives 
\begin{equation}
\FD \cdot \ex \approx 2 (\pup - \pdn)
\end{equation}

Therefore we have the relationship
\begin{equation}
\label{ResistDrag}
1/k_1 \approx \frac{1}{4 U}  \, \FD \cdot \ex
\end{equation}

>>>>

Integrating \eqref{q1} over the porous-medium domain $[-1, 1] \times [-1,1]$, applying the fundamental theorem of calculus, and rearranging gives
\begin{equation}
\label{eqn:k11}
k_{11} = \frac{2U}{\pup - \pdn}
\end{equation}
This exact formula gives the permeability in terms of the total flux $U$ and measurements of the upstream/downstream pressure.

@@

The hydrodynamic drag on the collection of bodies is obtained by integrating the surface traction over the boundary $\gamma$. The surface traction on a no-slip boundary is given by 
\begin{equation}
- \stress \, \nn = p \nn + \tau \ss
\end{equation}
where the negative sign is a consequence of choosing the normal vector $\nn$ to point out of the fluid region or {\em into} the bodies. The total drag on the collection of bodies is thus
\begin{equation}
\label{eqn:drag}
\FD =  - \int_{\gamma} \stress \, \nn \, ds =  \int_{\gamma} p \nn + \tau \ss \, ds
\end{equation}

@@

Projecting \eqref{divthm} onto $\ex$, using \eqref{eqn:drag}, and rearranging gives the exact relationship
\begin{equation}
\label{drag_press}
\FD \cdot \ex = \int_{-1}^{1} \left( -p(x,y) + 2 \mu u_x(x,y) \right) \big|_{x=-x_0}^{x=x_0} dy + 
\int_{-x_0}^{x_0} \mu u_y(x,y) \big|_{y=-1}^{y=1} dx
\end{equation}
We will now make some simplifying assumptions. First, because the imposed flow profile is uniform $\UU = (U,0)$, slip is permitted along the top and bottom boundaries $y=\pm 1$ and so the viscous stress will generally be much smaller than on the no-slip erodable boundaries. We will therefore drop the contribution from the second integral above. Second, if $x_0 > 1$ is chosen a sufficient distance from the erodable bodies, the flow profile will approximately match the uniform profile, implying that the term involving $u_x(\pm x_0, y)$ can be dropped. In addition, the pressure $p(\mp x_0, y)$ will approximately match the upstream and downstream values respectively. With these assumptions, \eqref{drag_press} simplifies to the approximate form
\begin{equation}
\FD \cdot \ex \approx 2 (\pup - \pdn)
\end{equation}
Combining with \eqref{eqn:k11} yields an approximate relationship between the horizontal components of permeability and drag 
\begin{equation}
\label{}
\frac{1}{k_{11}} \approx \frac{1}{4 U}  \, \FD \cdot \ex
\end{equation}

USEFUL FOR BENCHMARK

@@
